Multilevel computation of glacier geometry \\ from Stokes dynamics

### 2021-05-30 paper/msg.tex
Add a basic MCD figure.
Edits section 2.

The standard model for determining the geometry of glaciers is based in part upon a dynamical description of ice flow, namely a shear-thinning version of the Stokes equations.  This Glen-Stokes ice-dynamics model can only determine the free-surface glacier geometry when it is combined with the surface kinematical equation (SKE) and a form of climate input, namely the rate of accumulation of snow or ablation, i.e.~melting and runoff.  In this section we state the strong form of this ``coupled'' glacier geometry model in the steady-state case, which we call the steady ice geometry problem (SIGP).  The emphasis here is on the complementarity-problem nature of the SIGP, often not explicit in the glaciers literature (e.g.~as observed by \cite{SchoofHewitt2013}).  We then define its weak form, noting along the way several unknown aspects of the theory.  Section \ref{sec:evolution} gives the straightfoward extension of the steady case to a time-discretized evolving-geometry model, the implicit ice geometry problem (IIGP).

The SIGP is defined on a fixed, bounded map-plane region $\Omega \subset \RR^d$ (Figure \ref{fig:stokesdomain}).  We denote the map-plane variables as $x$ when $d=1$ and $x,y$ when $d=2$.  On $\Omega$ we assume that a climatic mass balance (CMB) function $a(x,y)$ is defined at every point, whether or not ice is present at that location.  In ice-free areas this function could be described as the ``potential'' CMB, namely the annual balance of snow accumulation and potential melt if ice were present \cite{Cogleyetal2011}, e.g.~as computed by energy balance in a climate or weather model.  Here we assume $a$ has units of ice thickness per time, equivalently ice volume per area (in $\Omega$) per time, compatible with our assumption of constant ice density below.  Also we assume there is a bed elevation function $b(x,y)$ defined everywhere on $\Omega$, which determines the topography upon which the glacier sits.  The functions $a$ and $b$ are the data (inputs) of the SIGP.

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.75\textwidth]{genfigs/stokesdomain.pdf}
\end{center}
\caption{In the steady ice geometry problem (SIGP) the CMB $a$ (arrows; downward $=$ accumulation) and bed elevation $b$ (solid) are given on a fixed map-plane region $\Omega \subset \RR^d$.  The solution includes a surface elevation $s$ (dashed) on $\Omega$; note $s=b$ where ice-free.  The ice velocity $\bu$ and pressure $p$ are defined in the icy domain: $\Lambda_s = \{(x,y,z)\,:\,b(x,y) < z < s(x,y)\} \subset \RR^{d+1}$.}
\label{fig:stokesdomain}
\end{figure}

The Glen-Stokes dynamical model, the so-called stress balance, for ice only applies in the icy domain in $\RR^{d+1}$.  We make a strong, but common \cite[for example]{IsaacStadlerGhattas2015,Jouvetetal2008,Lengetal2012,WirbelJarosch2020} assumption this this icy domain has a well-defined upper surface elevation, a function $s(x,y)$.  That is, we assume there are \emph{no overhangs}, and that the under-side of the ice is in contact with the bed $b$.  We then define $s$ everywhere in $\Omega$ by extending with $s=b$ where ice is absent, thus $s\ge b$ applies on $\Omega$.  Note that $s$ is part of the model solution; it is not given data.

However, as a consequence of the no-overhangs assumption, the SIGP as described here is likely not to be well-posed because of an issue at the ice margin.  There may be no steady state because the fluid in the vicinity of a steep ice margin, especially on a steep bed feature, ``wants'' to generate an overhang, violating the assumption that $s$ is well-defined.  Furthermore the same concern applies to each time step of an evolving model; the model does not stop overhangs from appearing at the margin.  However, because overhangs are small features in large glaciers and ice sheets, essentially all modeling literature ignores this possibility and assumes well-defined surface elevation and thickness \cite{Jouvetetal2008,Lengetal2012,WirbelJarosch2020}.  An exception is \cite{PralongFunk2005}, who furthermore suggest a potentially well-posed continuum model, a nontrivial extension of the one here, in which serac and ice-cliff calving occurs via a damage variable and a stress-fracture failure criterion.  This extended model also explains one of our numerical boundary variants, a short, fixed-height cliff (Section \ref{sec:mcdstokes}), but overhangs are not allowed in any of our numerical constructions.

Based on the assumption of a well-defined upper surface, we define the (solution) extent of the ice as the open set
\begin{equation}
\Lambda_s = \{(x,y,z)\,|\,(x,y) \in \Omega \,\text{ and }\, b(x,y) < z < s(x,y)\}  \subset \RR^{d+1}, \label{eq:lambdas}
\end{equation}
where $z$ is vertically-upward.  (If $d=1$ then coordinates are ``$(x,z)$'' on $\Lambda_s$.)  The map-plane region $\Omega$ need not be connected or simply-connected, but even if so the solution set $\Lambda_s$ need not be.  However, $\Lambda_s$ has the topology of the product of an open subset of $\Omega$ and an interval, and we will approximate it using an extruded mesh (Section \ref{sec:fe}).

For a given geometry $\Lambda_s$, we model the ice as a very-viscous \cite{Acheson1990}, non-Newtonian fluid subject to Glen's shear-thinning flow law \cite{GreveBlatter2009}; see also \cite[Chapter 1]{FowlerNg2021}.  Allowing any Glen exponent $n\ge 1$, the equations inside $\Lambda_s$ are
\begin{align}
- \nabla \cdot \tau + \nabla p &= \rhoi \bg &&\text{\emph{stress balance}} \label{eq:forcebalance} \\
\nabla \cdot \bu &= 0 &&\text{\emph{incompressibility}} \label{eq:incompressible} \\
\tau &= B_n |D\bu|^{(1/n) - 1} D\bu  &&\text{\emph{flow law}} \label{eq:viscflowlaw}
\end{align}
The solution fields here are the velocity $\bu$, pressure $p$, and deviatoric stress $\tau$.  Equations \eqref{eq:forcebalance} and \eqref{eq:viscflowlaw} form the momentum conservation (stress balance) model, while \eqref{eq:incompressible} is an aspect of our mass conservation model.  As seen below, mass conservation on the free surface of $\Lambda_s$ requires an additional equation \eqref{eq:ske}.

Regarding tensors and their notation, recall that the (Cauchy) stress tensor $\sigma$ decomposes into the deviatoric part $\tau$ minus the pressure, i.e.~$\sigma = \tau - p\,I$, so equation \eqref{eq:forcebalance} simply says $-\Div \sigma = \rhoi \bg$.  The strain rate tensor $D\bu$ is the symmetric part of $\grad \bu$, $D\bu = \frac{1}{2} \left(\grad\bu + \grad\bu^\top\right)$, and the tensor norm used in \eqref{eq:viscflowlaw} satisfies $|D\bu|^2 = \frac{1}{2} (D\bu)_{ij} (D\bu)_{ij}$.  Because $D\bu$ is symmetric, and because it has trace zero by equation \eqref{eq:incompressible}, i.e.~$\trace(D\bu)=\nabla \cdot \bu = 0$, equation \eqref{eq:viscflowlaw} implies that $\tau$ is also symmetric with trace zero, thus that $p=-(d+1)^{-1} \trace \sigma$.

In computations we will use constants $n=3$, ice density $\rhoi=910 \,\text{kg}\,\text{m}^{-3}$ \cite{Huybrechtsetal1996}, and gravity $\bg=\left<0,0,-g\right>$, with $g=9.81\,\text{m}\,\text{s}^{-2}$.  The ice hardness $B_n$ is a constant because we assume isothermal conditions \cite{GreveBlatter2009}, with $B_3=6.8082\times 10^7\,\text{Pa}\,\text{s}^{1/3}$ \cite{Huybrechtsetal1996}.

For the $n=1$ (Newtonian) Stokes equations one would write \eqref{eq:viscflowlaw} as $\tau = 2\nu D\bu$ with viscosity $\nu>0$, but exponents $n>1$ imply an effective viscosity function of $|D\bu|$.  This would thus be singular in the limit of small strain rates, and so, motivated by the actual finite viscosity of glacier ice \cite{GreveBlatter2009}, we define the regularized effective viscosity
\begin{equation}
\nu_\eps = \frac{1}{2} B_n \left(|D\bu|^2 + \eps\, D_0^2\right)^{(\pp-2)/2}, \label{eq:regeffvisc}
\end{equation}
where $\pp=(1/n)+1$, with $\pp=4/3$ in computations.  The constant $D_0$ defines a strain-rate scale for glacier flow; $D_0 = 1 \,\text{a}^{-1}$ and $\eps = 10^{-4}$ are used here.  Also we eliminate $\tau$ and rewrite \eqref{eq:forcebalance} as $- \nabla \cdot \left(2 \nu_\eps\, D\bu\right) + \nabla p = \rhoi \mathbf{g}$, with a vector $p$-Laplacian as the leading-order term.

Our SIGP model uses dynamic boundary conditions for isolated, grounded, and non-sliding ice.  In addition to the already-stated assumption that the top and bottom boundaries of $\Lambda_s$ can be identified, we further assume these surfaces have well-defined tangents.  On the upper free surface we set a condition of zero applied stress,
\begin{equation}
\left(2 \nu_\eps D\bu - pI\right) \bn_s = \bzero  \qquad \qquad \text{\emph{top} } \overline{\partial} \Lambda_s \label{eq:topbc}
\end{equation}
where $\bn_s$ is any normal to $\overline{\partial} \Lambda_s$.  (Providing a nonzero atmospheric pressure at the surface is straightforward, but it has no important consequence.)  On the base we impose no slip:
\begin{equation}
\bu = \bzero  \qquad\qquad \text{\emph{base} } \underline{\partial} \Lambda_s. \label{eq:basebc}
\end{equation}

Note that the ice flow extends in the horizontal direction until a free boundary at the glacier margin is reached, and the surface gradient $\grad s$ may become singular there, but the top and bottom surfaces are assumed to meet at the margin (Figure \ref{fig:stokesdomain}).  An alternative geometry with a small cliff is also considered (Section \ref{sec:fe}).  Real glacier margins may indeed occur as fracture-generated cliffs \cite{PralongFunk2005}, but fracture processes are not modeled here.

The well-posedness of the above dynamics model, for fixed domain $\Lambda_s$, is proven by \cite{JouvetRappaz2011}, and the solution is a unique pair $(\bu,p)$ defined on $\Lambda_s$.  (The function spaces are identified below when stating the weak formulation.)  However, the simultaneous determination of $\Lambda_s$ and $(\bu,p)$ is the goal of the SIGP model.  Indeed, the above equations make no reference to the climate input function $a$, so we need another ``equation'', which we will see is actually an inequality.

Noting that the surface elevation is already defined on all of $\Omega$, with $s=b$ off the ice, we also extend the surface normal $\bn_s$, thus we set
\begin{equation}
\bn_s = \left<-s_x,-s_y,1\right> \label{eq:surfacenormal}
\end{equation}
so that the (un-normalized) surface normal is specified almost everywhere on $\Omega$.  (By contrast, note that the dynamical boundary condition \eqref{eq:topbc} applies only on top of the ice.)  Furthermore we extend the surface value of the velocity to all of $\Omega$:
\begin{equation}
\bus(x,y) = \begin{cases} \bu(x,y,s(x,y)), & s(x,y) > b(x,y), \\
                     \bzero, & \text{elsewhere}. \end{cases} \label{eq:surfacevelocity}
\end{equation}
(The movement of the solid earth would determine $\bu|_b \ne 0$, thus $\bu|_s$ could be nonzero in ice-free areas, and a more-complete model could include this small effect.)

The steady-state surface kinematical equation (SKE) \cite[see equation (5.21)]{GreveBlatter2009} is the needed additional aspect of mass conservation:
\begin{equation}
\bus \cdot \bn_s + a = 0 \qquad \text{\emph{on the ice}}. \label{eq:ske}
\end{equation}
Note that $a(x,y)$ is the \emph{vertical} ice thickness added per time.  (Some references use a distinct quantity, namely the thickness added perpendicularly to the ice surface \cite{GreveBlatter2009}, which is significantly different if the gradient $\grad s$ is large.)

While the involved quantities are defined everywhere, kinematical balance \eqref{eq:ske} applies only \emph{on} the ice.  However $\bus \cdot \bn_s + a \le 0$ everywhere in $\Omega$ because $a$ is nonpositive in steady state in ice-free locations.  In fact, when combined with the constraint that $s\ge b$ everywhere on $\Omega$, SKE \eqref{eq:ske} is part of an infinite-dimensional nonlinear complementarity problem (NCP) \cite{Bueler2021conservation}.  Recall that an NCP on a finite-dimensional vector space $V=\RR^k$ combines the three statements $x\ge 0$, $F(x)\ge 0$, and $x F(x)=0$, where $F:V\to V$ \cite{FacchineiPang2003}.

@@

Jouvet and Rappaz \cite{JouvetRappaz2011} prove that this Glen-Stokes formulation is well-posed under the above assumptions if also the Neumann boundary is $C^1$.  In particular they show \eqref{eq:glenstokesweak} is equivalent to minimization of a convex and coercive functional over the divergence-free subspace, but also that there is a unique pressure $p\in L^\qq(\Lambda)$.

@@

>>>>

The standard model for determining the geometry of glaciers is based in part upon a dynamical description of ice flow, namely a shear-thinning version of the Stokes equations.  This Glen-Stokes ice-dynamics model can only determine the free-surface glacier geometry when it is combined with the surface kinematical equation (SKE) and a climate input, namely the balance of the rates of accumulation of snow and of ablation, i.e.~melting and runoff.  In this section we state the strong form of the resulting ``coupled'' glacier geometry model in the steady-state case, which we call the steady ice geometry problem (SIGP).  The emphasis here is on the complementarity-problem nature of the SIGP, which is often not explicit in the glaciers literature (e.g.~as observed by \cite{SchoofHewitt2013}).  We then define its weak form, noting along the way several unknown aspects of the theory.  Section \ref{sec:evolution} gives the straightfoward extension of the steady case to a time-discretized evolving-geometry model, the implicit ice geometry problem (IIGP).

The SIGP is defined on a fixed, bounded map-plane region $\Omega \subset \RR^d$ for $d=1,2$ (Figure \ref{fig:stokesdomain}).  The coordinates on $\Omega$ are denoted as $x$ when $d=1$ and $x,y$ when $d=2$.  On $\Omega$ we assume that a climatic mass balance (CMB) \cite{Cogleyetal2011} function $a(x,y)$ is defined at every point, whether or not ice is present at that location.  In ice-free areas this function is the ``potential'' CMB, namely the annual balance of snow accumulation and melt if ice were present, e.g.~as computed by energy balance in a climate or weather model.  Here we assume $a$ has units of ice thickness per time, compatible with our assumption of constant ice density (below).  Next we assume there is a bed elevation function $b(x,y)$ defined everywhere on $\Omega$, which determines the topography upon which the glacier sits.  The functions $a$ and $b$ are the data (inputs) of the SIGP.

\begin{figure}[t]
\begin{center}
\includegraphics[width=0.7\textwidth]{genfigs/stokesdomain.pdf}
\end{center}
\caption{In the SIGP the CMB $a$ (arrows; down for accumulation) and bed elevation $b$ (solid) are given data on a map-plane region $\Omega \subset \RR^d$.  The solution includes a surface elevation $s$ (dashed) on $\Omega$, such that $s\ge b$, plus the ice velocity $\bu$ and pressure $p$ on the icy domain $\Lambda_s = \{b < z < s\} \subset \RR^{d+1}$.}
\label{fig:stokesdomain}
\end{figure}

The Glen-Stokes dynamical model, the so-called stress balance, only applies in the icy domain in $\RR^{d+1}$.  We make a strong, but common \cite[for example]{IsaacStadlerGhattas2015,Jouvetetal2008,Lengetal2012,WirbelJarosch2020} assumption this this icy domain has a well-defined upper surface elevation, a function $s(x,y)$.  That is, we assume there are \emph{no overhangs}, and that the under-side of the ice is in contact with the bed $b$.  We then define $s$ everywhere in $\Omega$ by extending with $s=b$ where ice is absent, thus $s\ge b$ applies on all of $\Omega$.  Note that $s$ is part of the model solution; it is not given data.

However, as a consequence of the no-overhangs assumption, the SIGP as described here is likely not to be well-posed because of an issue at the ice margin.  There may be no steady state because the fluid in the vicinity of a steep ice margin, especially on a steep bed feature, ``wants'' to generate an overhang, violating the assumption that $s$ is well-defined.  Furthermore the same concern applies to each time step of an evolving model; actual glaciers can develop overhangs at the margin.  However, because overhangs are small features in large glaciers and ice sheets, essentially all modeling literature ignores this possibility and assumes well-defined surface elevation and thickness \cite{Jouvetetal2008,Lengetal2012,WirbelJarosch2020}.  An exception is \cite{PralongFunk2005}, who suggest a potentially well-posed continuum model, a nontrivial extension of the one here, in which serac and ice-cliff calving occurs via a damage variable and a stress-fracture failure criterion.  Though marginal cliffs may exist in our model (Section \ref{sec:fe}), overhangs are never allowed.

Based on a well-defined upper surface, the icy domain is the open set
\begin{equation}
\Lambda_s = \{(x,y,z)\,|\,(x,y) \in \Omega \,\text{ and }\, b(x,y) < z < s(x,y)\}  \subset \RR^{d+1}, \label{eq:lambdas}
\end{equation}
where $z$ is vertically-upward.  (Coordinates are denote $(x,z)$ on $\Lambda_s$ when $d=1$.)  The domain $\Lambda_s$ has the topology of the product of an open subset of $\Omega$ and an interval, and we will approximate it using an extruded mesh (Section \ref{sec:fe}).  Again note $\Lambda_s$ is part of the solution.

We model the ice as an incompressible, very-viscous \cite{Acheson1990}, non-Newtonian fluid subject to Glen's shear-thinning flow law \cite{GreveBlatter2009}; see also \cite[Chapter 1]{FowlerNg2021}.  Allowing any Glen exponent $n\ge 1$, the equations inside $\Lambda_s$ are
\begin{align}
- \nabla \cdot \tau + \nabla p &= \rhoi \bg &&\text{\emph{stress balance}} \label{eq:forcebalance} \\
\nabla \cdot \bu &= 0 &&\text{\emph{incompressibility}} \label{eq:incompressible} \\
\tau &= B_n |D\bu|^{(1/n) - 1} D\bu  &&\text{\emph{flow law}} \label{eq:viscflowlaw}
\end{align}
The solution fields here are the velocity $\bu$, pressure $p$, and deviatoric stress $\tau$.  Equations \eqref{eq:forcebalance} and \eqref{eq:viscflowlaw} form the momentum conservation (stress balance) model, while \eqref{eq:incompressible} follows from constant density and mass conservation.

Regarding tensors and their notation, recall that the (Cauchy) stress tensor $\sigma$ decomposes into the deviatoric part $\tau$ minus the pressure, i.e.~$\sigma = \tau - p\,I$, so equation \eqref{eq:forcebalance} simply says $-\Div \sigma = \rhoi \bg$.  The strain rate tensor $D\bu$ is the symmetric part of $\grad \bu$, $D\bu = \frac{1}{2} \left(\grad\bu + \grad\bu^\top\right)$, and the tensor norm used in \eqref{eq:viscflowlaw} satisfies $|D\bu|^2 = \frac{1}{2} (D\bu)_{ij} (D\bu)_{ij}$.  Because $D\bu$ is symmetric, and because it has trace zero by equation \eqref{eq:incompressible}, i.e.~$\trace(D\bu)=\nabla \cdot \bu = 0$, equation \eqref{eq:viscflowlaw} then implies that $\tau$ is also symmetric with trace zero, thus that $p=-(d+1)^{-1} \trace \sigma$.

In computations we will use constants $n=3$, ice density $\rhoi=910 \,\text{kg}\,\text{m}^{-3}$ \cite{Huybrechtsetal1996}, and gravity $\bg=\left<0,0,-g\right>$, with $g=9.81\,\text{m}\,\text{s}^{-2}$.  The ice hardness $B_n$ is a constant because we assume isothermal conditions \cite{GreveBlatter2009}, with the value $B_3=6.8082\times 10^7\,\text{Pa}\,\text{s}^{1/3}$ \cite{Huybrechtsetal1996} used in computations.

For the $n=1$ (Newtonian) Stokes equations one would write \eqref{eq:viscflowlaw} as $\tau = 2\nu D\bu$ with viscosity $\nu>0$, but exponents $n>1$ imply an effective viscosity function of $|D\bu|$.  This would be singular in the limit of small strain rates, and so, motivated by the actual finite viscosity of glacier ice \cite{GreveBlatter2009}, we define the regularized effective viscosity using $\eps>0$,
\begin{equation}
\nu_\eps = \frac{1}{2} B_n \left(|D\bu|^2 + \eps\, D_0^2\right)^{(\pp-2)/2}, \label{eq:regeffvisc}
\end{equation}
where $\pp=(1/n)+1$, with $\pp=4/3$ in computations.  The constant $D_0$ defines a strain-rate scale for glacier flow; values $D_0 = 1 \,\text{a}^{-1}$ and $\eps = 10^{-4}$ are used in computations.

Our SIGP model uses dynamic boundary conditions for isolated, grounded, and non-sliding glaciers.  (Floating and sliding cases are topics for additional research.)  In addition to the already-stated assumption that the top and bottom boundaries of $\Lambda_s$ can be identified, we further assume these surfaces have well-defined tangents.  On the base we impose no slip:
\begin{equation}
\bu = \bzero  \qquad\qquad \text{\emph{base} } \Gamma_0. \label{eq:basebc}
\end{equation}
On the other sub-aerial surfaces we set a condition of zero applied stress,
\begin{equation}
\left(2 \nu_\eps D\bu - pI\right) \bn = \bzero  \qquad \qquad \text{\emph{top and cliffs (if present)}} \label{eq:topbc}
\end{equation}
where $\bn$ is any normal to $\overline{\partial} \Lambda$.  (A nonzero atmospheric pressure at the surface is straightforward to apply if desired.)  Note that the ice flow extends in the horizontal direction until a free boundary at the glacier margin is reached, but that $\grad s$ may become singular there.

The simultaneous determination of $\Lambda_s$ and $(\bu,p)$ is the goal of the SIGP model.  However, the above equations make no reference to the climate input function $a$, so we need another ``equation'', one which is actually an inequality.  Noting that the surface elevation is already defined on all of $\Omega$, with $s=b$ off the ice, we set
\begin{equation}
\bn_s = \left<-s_x,-s_y,1\right> \label{eq:surfacenormal}
\end{equation}
as an (un-normalized) top-surface normal almost everywhere on $\Omega$.  Furthermore we extend the surface value of the velocity to all of $\Omega$:
\begin{equation}
\bus(x,y) = \begin{cases} \bu(x,y,s(x,y)), & s(x,y) > b(x,y), \\
                     \bzero, & \text{elsewhere}. \end{cases} \label{eq:surfacevelocity}
\end{equation}
A discontinuity of this function is allowed at the ice margin.

The steady-state surface kinematical equation (SKE) \cite[equation (5.21)]{GreveBlatter2009} is the needed additional aspect of mass conservation:
\begin{equation}
\bus \cdot \bn_s + a = 0 \qquad \text{\emph{on the ice}}. \label{eq:ske}
\end{equation}
Note that $a(x,y)$ is the \emph{vertical} ice thickness added per time, while some references use a distinct quantity, namely the thickness added perpendicularly to the ice surface, significantly different if $\grad s$ is large.

Though kinematical balance \eqref{eq:ske} applies only on the ice, $\bus \cdot \bn_s + a \le 0$ applies everywhere in $\Omega$ because $a$ is nonpositive in steady state in ice-free locations.  In fact, when combined with the constraint that $s\ge b$ everywhere on $\Omega$, SKE \eqref{eq:ske} is part of an infinite-dimensional nonlinear complementarity problem (NCP) \cite{Bueler2021conservation}.  Recall that an NCP on a finite-dimensional vector space $V=\RR^k$ combines the three statements
\begin{equation}
x\ge 0, \quad F(x)\ge 0, \quad x F(x)=0 \label{eq:ncp}
\end{equation}
for all $x\in V$, where $F:V\to V$ \cite{FacchineiPang2003}.

@@

Jouvet and Rappaz \cite{JouvetRappaz2011} prove that this fixed-domain Glen-Stokes formulation is well-posed under the above assumptions if also the Neumann boundary is $C^1$.  In particular they show \eqref{eq:glenstokesweak} is equivalent to minimization of a convex and coercive functional over the divergence-free subspace, but also that there is a unique pressure $p\in L^\qq(\Lambda)$.

@@

FIXME Figure \ref{fig:decompclassical} shows such a decomposition

% figure generated in mg-glaciers/py by using decomposition_plain() in visualize.py and then:
% $ ./obstacle.py -J 5 -jcoarse 1 -irtol 1.0e-5 -monitor -diagnostics -random -randommodes 15 -o classical.pdf
% to get decomp_classical.pdf
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.7\textwidth]{fixfigs/decompclassical.pdf}
\end{center}
\caption{An example $d=1$ and $J=4$ MCD decomposition of the defect obstacle $\chi^J$ for an iterate $s^J$.}
\label{fig:decompclassical}
\end{figure}
